Alleviating the Topology Mismatch Problem in Unstructured and Structured P2P Overlay Networks: A Survey

### 2014-01-23 structured.tex
2012.07.12 (Vassilis) Merged introduction section. Sectioning according to the method an algorithm is using dropped (almost all use a combination of two or more). First attempt for the tabular data on an external file.

\section{Decentralized Structured Algorithms}
\label{section:structured}

@@

%{\sethlcolor{yellow}\hl{HA:  Talk about Tapestry, Pastry, CAN and Chord briefly here!}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Geographic Layout} \label{section:geographic_layout}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Global Soft-State}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Mithos}
\emph{Mithos} \cite{waldvogel_mythos_2003} is a P2P protocol which incorporates
directed incremental probing to find near optimal node placement, and is
classified by its authors as an integration of geographic layout and proximity
routing overlay optimization methods.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf LAPTOP}
\emph{LAPTOP} \cite{wu_laptop_2007}, organises the overlay into a tree-based
hierarchy with main focus on reducing hops during message routing as well as
minimizing maintenance overhead. Additionally, a caching scheme is also
incorporated so as to further reduce routing table update costs. The authors
theoretically show that in LAPTOP routing path length is bounded by $O(log_d N)$
and node joining and leaving in the overlay network is bounded by
$O\left( d log_d N \right)$ hops in a balanced overlay tree, where $N$ is the
number of nodes, and $d$ is the maximum degree of each node. LAPTOP implements
the geographical layout approach  and constructs its layout in a self-organizing
and efficient fashion, by estimating the round-trip times to a small number of
nodes in the overlay network in order to make them roughly aware of their
physical distances among them.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Proximity Routing}
\label{section:pr}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Proximity in Kademlia}
% Before discussing {\em Proximity in Kademlia}, it would be helpful to briefly
% summarize the highlights about the {\em Kademlia} protocol. {\em Kademlia}
% \cite{maymounkov_kademlia_2002} is a distributed hash table (DHT) based
% protocol for P2P networks, which uses an iteration based lookup algorithm. The
% protocol uses the standard $160$ bit ID system for nodes and locates the nodes
% in a prefix binary tree, where IDs are used as prefixes. The iterative lookup
% operations are done over this prefix binary tree, which converges to
%logarithmic
% lookup times. The ID's are assigned randomly, therefore in Kademlia, there is
%no
% proximity control, which results in inefficient use of the underlying network
% during lookup and retrieve operations.

\emph{Proximity in Kademlia} \cite{kaune_pkad_2008} introduces proximity
controls over the vanilla Kademlia protocol's random ID assignment, in order to
optimize the underlying network usage of the protocol. The work in this paper
can also be considered, as a more generic study over building proximity in the
context of iterative lookup algorithms. Focus is given on both the overlay and
the underlaying tiers in the sense that in the first improves the routing
performance according to a cost metric that is provided by the later and
quantifies the suitability of establishing a communication link between peers as
a cost function, based on the used proximity criteria (RTT, ISP locality, etc.).
%An underlay metric provides information about the underlay network. The paper
%  distingushes between three kinds of possibilities to quantify it:
%\begin{itemize}
% \item Using measurements gained by previous lookups
% \item Using measurements acquired by other peers or jointly calculated with
%  others
% \item Using a local database to look up information
%\end{itemize}
The paper proposes two approaches for overlay optimisation. One falling into
{\em proximity routing} and the other on {\em proximity neighbour selection}
(see Section~\ref{section:pns}) approaches overlay optimization techiques for
exploiting proximity. For the first, the goal is in choosing the best next hop
during routing a message. Due to the fact that the routing in Kademlia is
iterative, it is the initiator of the lookup that chooses each next hop from a
set of candidate nodes. Standard Kedemlia always chooses the closest node with
respect to the XOR metric but with proximity routing selection, Kademlia
chooses the one with the smallest underlay metric cost. Thus, as in all such
approaches, there is a trade-off between the overlay and underlay distances.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf CHOord considering Proximity on IPv6 (CHOP6)}
\emph{CHOP6} \cite{morimoto_chop6_2007} roughly estimates the proximity among
nodes by exploiting the IPv6 address format and RTT information if available.
The proximity estimation is achieved by introducing a 64-bit ID scheme in which
the least significant bit part is the IPv6 global routing prefix and thus
enabling a longest prefix match scheme. The protocol is designed based on the
observation that it is possible to estimate a node's geographical location by
simply examining the upper 32-bits of its IPv6 address. Moreover, similar to
Chord, CHOP6 uses a finger table, whose entries hold more than
one candidate node.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf T2MC}
T2MC \cite{shi_t2mc_2008} uses traceroute logs to detect different autonomous
systems and cluster close by peers, thus reducing redundant traffic that crosses
autonomous system boundaries. T2MC uses a customized k-mean classification
algorithm with $k=2$ to perform the classification, and exploits the stable
structure of the Internet routers to guide clustering. The peer chooses the
minimum and maximum Latency results from the traceroute to initialize the
centroinds of two sets. Then the peer calculates, for all hops allong its
tracerouted path, the absolute distance to these centroids of both sets and
assigns the routers to that centroid with which it has the smaller absolute
distance. After that, the mean and variance values are calculated and if the
variance is larger than a predefined threshold then the algorithm sets the two
latency mean values as new centroids for the two sets and loops again.
Ultimately peer will end up with two sets having the minimum intra-set variance.
The peer, then, chooses the router from the second set with the minimum hops
attribute and sets it as a threshold. The selected router and all others whose
hops attribute is larger than the threshold are classified as \emph{remote}
router cluster. The remaining are classified as \emph{near}. From the near
class, the peer chooses the one with maximum hops attribute as its edge router,
and registers it along with the all the near cluster into the DHT of the P@P
overlay. As new peers join the network, those that share the same edge router
or any of the members of the near router clustersm there would gather to form a
close peer cluster. As Edge routers can provide more valuable information than
other members of the near set, T2MC was designed to prioritize interaction of
peers and edge gateways.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf PChord}
\emph{PChord}\cite{hong_pchord_2005} is a based on the Chord DHT which adds
proximity routing into its routing mechanism. The main modification over the
vanilla Chord is the inclusion of a \emph{proximity list} into its routing table
so that the next hop is decided based not only by considering best progress
towards the key, but on the physical proximity of the candidate nodes as well.
The list is, at join time, empty but as the PChord node starts to interact with
other nodes it applies a heuristic mechanism to fill up the list. Entries are
dynamicaly added or removed as the network state changes. Due to the fact that,
with each step, there is always progress towards the target node in the ID
space, PChord will result in a reduced hop number than Chord, since each hop in
PChord is larger or at least equal in the key space. Passing through proximity
links in the underlaying network means reduced routing cost. Additionally, if
the number of entries in the proximity list is the same as the number of network
partitions, PChord prevents hops from jumping in and out the network partition
the current node belongs to.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf AChord}
\emph{AChord} \cite{dao_achord_2006} uses IPv6's anycast mechanism in order to
releave the protocol from complex joining procedures, and achieve high accuracy
of network proximity giving high routing efficiency, Anycast delivers a message
comming from the outside of an anycast group to the physicaly closest node in
that group. AChord organizes all nodes participating in the overlay network into
an anycast group. Any joining node comes outside of that group and, thus, is
automaticaly forwarded to the physicaly nearest node in order to bootstrap,
avoiding the need to, explicitly, maintain such nodes, and the effort of finding
a way of locating the physically nearest among them. The ID of the new comming
node is computed based on the ID of the bootstrap node and the bootstrap's
predecessor in a way that the constructed ID will be positioned between the
aformentioned two. After joining, the finger table is build the same way as in
the Chord protocol. Moreover, additional nodes are maintained in a structure
called \emph{neighbourship table} which stores information about the closest
known node. The routing decision is made by using both the neighbourship and
the finger table. The authors claim this to be a lightweight approach that
requires few changes to Chord in order not to affecting its own advantageous
characteristics.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Chord6}
\emph{Chord6} \cite{xiong_chord6_2005} is another Chord variant that tries to
exploit the hierarchical features of IPv6 in order to create a substrate that
reduces interdomain traffic between service providers. The difference between
Chord6 and Chord the identifier definition. Therefore, the approach can be
easily portable to other DHTs such as CAN, Pastry and Tapestry. In Chord6 the
identifier contains two parts: the higher bits are obtained by hashing the
node's IPv6 address prefix of specific length, while the remaining lower bits
are the hash value of the rest of that IPv6 address. As a result of this
assignment, nodes in a domain will be mapped onto a continuous key space on the
overlay network, which avoids unnecessary message forwarding across different
service providers, thus minimising overall routing cost.

%
% TODO: SOME DISCUSSION
%       RECHECK VALIDITY
%
% However, even though nodes in the same domain would have close identifiers,
% nodes in two close domains may have very different ones.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Proximity Neighbour Selection}
\label{section:pns}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Proximity in Kademlia}
As already mentioned on the the corresponding paragraph when discussing
proximity routing approaches (see Section~\ref{section:pr}), the paper
proposes \emph{proximity neighbour selection} method, as well, for overlay
optimisation. The goal, according to this, is to keep peers with the least
contact cost in the routing table. As Kademlia constantly learns new peers
(incoming requests, through iterative lookup) no special algorithm for
searching more cost effective peers is necessary and simply choose the best
peers seen so far. For more information on the Proximity in Kademlia please
consult the paragraph in Section~\ref{section:pr}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf DHT-PNS}
The work in \cite{hancong_pnsbased_2006} propose a proximity neighbour selection
scheme on top of the Chord DHT. The main goal is to use proximity information
to group physically close by nodes as neighbours in the DHT table. In order to
detect proximity, virtual network coordinates of peers are used, by using the
Vivaldi protocol \cite{cox_vivaldi_2004}. The virtual coordinates are then used
by the nodes to map to identifier space in the DHT. The space is partitioned
using a \emph{concentric circle clustering scheme} where successive cycles of
radiuses $\rho$, $2\rho$, $3\rho$ and so on, are constructed. Then the formed
annuluses are divided into $2\chi-1$ \emph{sectors}, where $\chi$ denotes the
sequence number of the annulus starting from $\chi = 1$ for the centre cycle. It
is proved in the paper, that this way each sector occupies the same area as does
the center cycle. Assuming uniform node distribution, this characteristic,
favours a more load balanced clustering operation. Every sector in this $2d$
coordinate space is mapped to a unique \emph{region} in the DHT space forming a
multi-layer node identifier space.  Thus, any nodes that belong to the same
sector, are mapped to the same region as well, preserving their proximity
relationship unveiled by the use of the Vivaldi protocol. The individual pieces
are mapped to the identifier space uniquely, allowing logarithmic lookup
operations with high probability on Chord. The system described in the previous
section allows any node to obtain its DHT key and its region key, in a fully
distributed manner, just by applying a consistent hash function. Using an RPC
call in Chord, the node can obtain the region's master node, called
\emph{Cluster Node (CN)} which is responsible for clustering the nodes belonging
in the same sector or region with that of the node at hand. An additional RPC
call, registers it to its corresponding region and publishes its information,
through the special peer CN. The node can, additionaly, ask CN for other
nodes that have previously joined the region in order to add them into its
neighbour set for future routing table optimization. Even in the case when no
neighbour is detected in the current region, the search is expanded to adjasent
regions and towards an upper layer identifier space until one is found or the
first layer reached.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Quasi-Chord}
The approach that is proposed by Sun and Zhang in \cite{sun_quasi_2008}
confronts the topology mismatch problem, in the Chord DHT context which, in its
vanilla version, takes no consiteration for the underlying physical network
topology during the construction of the identifier cycle. To construct a
\emph{Quasi-Chord} network three steps are followed needed. First, each host
acquires its coordinates in the geometric space utilizing the \emph{global
network position (GNP)} protocol \cite{ng_gnp_2001}. Second, using the
\emph{Cantor space filling curve}, the $2$-dimensional space is converted to a
$1$-dimensional one, used in the last, third, step to build the Quasi-Chord
circle according to the host's Cantor value. In the following paragraphs,
these steps are furtherly discussed.

%
%\paragraph{GNP coordinates}
%First of all the host must be positioned in the geometric space. The algoritm
%  models the P2P network with a well defined distance function in such a way,
% it can predict, with high accuracy, the distance between any two points in the
% space by just evaluating the output of the distance function on the
% coordinates of these points. This is accomplished with the \emph{global
% network position (GNP)} protocol which\begin{inparaenum}[\itshape i\upshape)]
%  \item creates a reference set of $N$ landmark nodes so as to minimize the
%  error of ICMP measured distances and coordinate computed ones between them,
% and then
%  \item each host is able to measure its round-trip times to the $N$ Landmarks
% in order to compute its own coordinates.
%\end{inparaenum}
%
%\paragraph{Cantor SPF}
%After the $2$-d coordinates are set, in the next stage of the algorithn, each
%  participating peer is assigned a Cantor value, according to the application
% of a \emph{space filling curve} on the coordinate space. (TODO: add figure).
% This results in the conversion of the $2$-dimensional space to a
% $1$-dimensional Cantor space that can more easily be more mapped to the Chord
% hierarchy.
%
%\paragraph{Quasi-Chord construction}
%As can intuitively be infered by observing the Cantor chart, close-by nodes in
%  the physical layer, are more likely to have similar Cantor values. This
% attribute is exploited in order to construct a topology-aware identifier space
% for the Chord DHT. The cycle is constructed by sorting nodes in ascending
% order. Each host maintains 2 finger tables, one for clockwise and one for
% counter-clockwise stepping. This helps with the connectivity of the network
% because its not allowed to connect the first node with the last one since this
% will incur heavy traffic to the later\footnote{After all their Cantor values
% denote that they are actually the furthest of each other.}.
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf IP-based Clustering (IPBC)}
Proximity neighbour selection algorithms use probing and other techniques to
detect proximity. However, such methods are either not precise enough, or
overload the network. \emph{IP-based clustering} \cite{karwaczynski_ipbc_2007}
is a proximity neighbour selection based algorithm in which the authors propose
to use the IP address prefixes (16 bit for IPv4) in order to detect proximity.
\cite{freedman_iploc_2005} states that $97\%$ of prefixes larger than $24$ bits
belong to a single geographical location. However, using less number of bits
creates less precise results and more number of bits increase the burden on the
network and reduce the possible number of neighbours. Therefore, a careful
selection is required in terms of performance/accuracy tradeoff. IP-based
Clustering generates a key and its prefix and stores the later in the DHT
itself, so that any newly joining nodes with the same IP prefix can query it and
identify all the neighbours with the same one relatively easy. Nodes
periodically update their entries in the DHT by removing those who leave, or
those who has been timed out with no further activity detected from the node.

>>>>

\section{Decentralized Structured Architectures}
\label{section:structured}

@@

\subsection{Algorithms for Structured Architectures}

%###############################################################################
%###############################################################################
%###############################################################################
%       GEGRAPHIC LAYOUT
%###############################################################################
%###############################################################################
%###############################################################################

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Global Soft-State}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Mithos}
\emph{Mithos} \cite{waldvogel_mythos_2003} is a P2P protocol which incorporates
directed incremental probing to find near optimal node placement, and is
classified by its authors as an integration of geographic layout and proximity
routing overlay optimization methods.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{LAPTOP}
\emph{LAPTOP} \cite{wu_laptop_2007}, organises the overlay into a tree-based
hierarchy with main focus on reducing hops during message routing as well as
minimizing maintenance overhead. Additionally, a caching scheme is also
incorporated so as to further reduce routing table update costs. The authors
theoretically show that in LAPTOP routing path length is bounded by $O(log_d N)$
and node joining and leaving in the overlay network is bounded by
$O\left( d log_d N \right)$ hops in a balanced overlay tree, where $N$ is the
number of nodes, and $d$ is the maximum degree of each node. LAPTOP implements
the geographical layout approach  and constructs its layout in a self-organizing
and efficient fashion, by estimating the round-trip times to a small number of
nodes in the overlay network in order to make them roughly aware of their
physical distances among them.

@@

%###############################################################################
%###############################################################################
%###############################################################################
%       PROXIMITY ROUTING
%###############################################################################
%###############################################################################
%###############################################################################

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Proximity in Kademlia}
% Before discussing {\em Proximity in Kademlia}, it would be helpful to briefly
% summarize the highlights about the {\em Kademlia} protocol. {\em Kademlia}
% \cite{maymounkov_kademlia_2002} is a distributed hash table (DHT) based
% protocol for P2P networks, which uses an iteration based lookup algorithm. The
% protocol uses the standard $160$ bit ID system for nodes and locates the nodes
% in a prefix binary tree, where IDs are used as prefixes. The iterative lookup
% operations are done over this prefix binary tree, which converges to
%logarithmic
% lookup times. The ID's are assigned randomly, therefore in Kademlia, there is
%no
% proximity control, which results in inefficient use of the underlying network
% during lookup and retrieve operations.

\emph{Proximity in Kademlia} \cite{kaune_pkad_2008} introduces proximity
controls over the vanilla Kademlia protocol's random ID assignment, in order to
optimize the underlying network usage of the protocol. The work in this paper
can also be considered, as a more generic study over building proximity in the
context of iterative lookup algorithms. Focus is given on both the overlay and
the underlaying tiers in the sense that in the first improves the routing
performance according to a cost metric that is provided by the later and
quantifies the suitability of establishing a communication link between peers as
a cost function, based on the used proximity criteria (RTT, ISP locality, etc.).
%An underlay metric provides information about the underlay network. The paper
%  distingushes between three kinds of possibilities to quantify it:
%\begin{itemize}
% \item Using measurements gained by previous lookups
% \item Using measurements acquired by other peers or jointly calculated with
%  others
% \item Using a local database to look up information
%\end{itemize}
The paper proposes two approaches for overlay optimisation. One falling into
{\em proximity routing} and the other on {\em proximity neighbour selection}
approaches overlay optimization techiques for
exploiting proximity. For the first, the goal is in choosing the best next hop
during routing a message. Due to the fact that the routing in Kademlia is
iterative, it is the initiator of the lookup that chooses each next hop from a
set of candidate nodes. Standard Kedemlia always chooses the closest node with
respect to the XOR metric but with proximity routing selection, Kademlia
chooses the one with the smallest underlay metric cost. Thus, as in all such
approaches, there is a trade-off between the overlay and underlay distances.

@@

As already mentioned the paper
proposes \emph{proximity neighbour selection} method, as well, for overlay
optimisation. The goal, according to this, is to keep peers with the least
contact cost in the routing table. As Kademlia constantly learns new peers
(incoming requests, through iterative lookup) no special algorithm for
searching more cost effective peers is necessary and simply choose the best
peers seen so far.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{CHOord considering Proximity on IPv6 (CHOP6)}
\emph{CHOP6} \cite{morimoto_chop6_2007} roughly estimates the proximity among
nodes by exploiting the IPv6 address format and RTT information if available.
The proximity estimation is achieved by introducing a 64-bit ID scheme in which
the least significant bit part is the IPv6 global routing prefix and thus
enabling a longest prefix match scheme. The protocol is designed based on the
observation that it is possible to estimate a node's geographical location by
simply examining the upper 32-bits of its IPv6 address. Moreover, similar to
Chord, CHOP6 uses a finger table, whose entries hold more than
one candidate node.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{T2MC}
T2MC \cite{shi_t2mc_2008} uses traceroute logs to detect different autonomous
systems and cluster close by peers, thus reducing redundant traffic that crosses
autonomous system boundaries. T2MC uses a customized k-mean classification
algorithm with $k=2$ to perform the classification, and exploits the stable
structure of the Internet routers to guide clustering. The peer chooses the
minimum and maximum Latency results from the traceroute to initialize the
centroinds of two sets. Then the peer calculates, for all hops allong its
tracerouted path, the absolute distance to these centroids of both sets and
assigns the routers to that centroid with which it has the smaller absolute
distance. After that, the mean and variance values are calculated and if the
variance is larger than a predefined threshold then the algorithm sets the two
latency mean values as new centroids for the two sets and loops again.
Ultimately peer will end up with two sets having the minimum intra-set variance.
The peer, then, chooses the router from the second set with the minimum hops
attribute and sets it as a threshold. The selected router and all others whose
hops attribute is larger than the threshold are classified as \emph{remote}
router cluster. The remaining are classified as \emph{near}. From the near
class, the peer chooses the one with maximum hops attribute as its edge router,
and registers it along with the all the near cluster into the DHT of the P2P
overlay. As new peers join the network, those that share the same edge router
or any of the members of the near router clustersm there would gather to form a
close peer cluster. As Edge routers can provide more valuable information than
other members of the near set, T2MC was designed to prioritize interaction of
peers and edge gateways.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{PChord}
\emph{PChord}\cite{hong_pchord_2005} is a based on the Chord DHT which adds
proximity routing into its routing mechanism. The main modification over the
vanilla Chord is the inclusion of a \emph{proximity list} into its routing table
so that the next hop is decided based not only by considering best progress
towards the key, but on the physical proximity of the candidate nodes as well.
The list is, at join time, empty but as the PChord node starts to interact with
other nodes it applies a heuristic mechanism to fill up the list. Entries are
dynamicaly added or removed as the network state changes. Due to the fact that,
with each step, there is always progress towards the target node in the ID
space, PChord will result in a reduced hop number than Chord, since each hop in
PChord is larger or at least equal in the key space. Passing through proximity
links in the underlaying network means reduced routing cost. Additionally, if
the number of entries in the proximity list is the same as the number of network
partitions, PChord prevents hops from jumping in and out the network partition
the current node belongs to.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{AChord}
\emph{AChord} \cite{dao_achord_2006} uses IPv6's anycast mechanism in order to
releave the protocol from complex joining procedures, and achieve high accuracy
of network proximity giving high routing efficiency, Anycast delivers a message
comming from the outside of an anycast group to the physicaly closest node in
that group. AChord organizes all nodes participating in the overlay network into
an anycast group. Any joining node comes outside of that group and, thus, is
automaticaly forwarded to the physicaly nearest node in order to bootstrap,
avoiding the need to, explicitly, maintain such nodes, and the effort of finding
a way of locating the physically nearest among them. The ID of the new comming
node is computed based on the ID of the bootstrap node and the bootstrap's
predecessor in a way that the constructed ID will be positioned between the
aformentioned two. After joining, the finger table is build the same way as in
the Chord protocol. Moreover, additional nodes are maintained in a structure
called \emph{neighbourship table} which stores information about the closest
known node. The routing decision is made by using both the neighbourship and
the finger table. The authors claim this to be a lightweight approach that
requires few changes to Chord in order not to affecting its own advantageous
characteristics.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Chord6}
\emph{Chord6} \cite{xiong_chord6_2005} is another Chord variant that tries to
exploit the hierarchical features of IPv6 in order to create a substrate that
reduces interdomain traffic between service providers. The difference between
Chord6 and Chord the identifier definition. Therefore, the approach can be
easily portable to other DHTs such as CAN, Pastry and Tapestry. In Chord6 the
identifier contains two parts: the higher bits are obtained by hashing the
node's IPv6 address prefix of specific length, while the remaining lower bits
are the hash value of the rest of that IPv6 address. As a result of this
assignment, nodes in a domain will be mapped onto a continuous key space on the
overlay network, which avoids unnecessary message forwarding across different
service providers, thus minimising overall routing cost.

%
% TODO: SOME DISCUSSION
% However, even though nodes in the same domain would have close identifiers,
% nodes in two close domains may have very different ones.

%###############################################################################
%###############################################################################
%###############################################################################
%       PROXIMITY NEIGHBOUR SELECTION
%###############################################################################
%###############################################################################
%###############################################################################

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{DHT-PNS}
The work in \cite{hancong_pnsbased_2006} propose a proximity neighbour selection
scheme on top of the Chord DHT. The main goal is to use proximity information
to group physically close by nodes as neighbours in the DHT table. In order to
detect proximity, virtual network coordinates of peers are used, by using the
Vivaldi protocol \cite{cox_vivaldi_2004}. The virtual coordinates are then used
by the nodes to map to identifier space in the DHT. The space is partitioned
using a \emph{concentric circle clustering scheme} where successive cycles of
radiuses $\rho$, $2\rho$, $3\rho$ and so on, are constructed. Then the formed
annuluses are divided into $2\chi-1$ \emph{sectors}, where $\chi$ denotes the
sequence number of the annulus starting from $\chi = 1$ for the centre cycle. It
is proved in the paper, that this way each sector occupies the same area as does
the center cycle. Assuming uniform node distribution, this characteristic,
favours a more load balanced clustering operation. Every sector in this $2d$
coordinate space is mapped to a unique \emph{region} in the DHT space forming a
multi-layer node identifier space.  Thus, any nodes that belong to the same
sector, are mapped to the same region as well, preserving their proximity
relationship unveiled by the use of the Vivaldi protocol. The individual pieces
are mapped to the identifier space uniquely, allowing logarithmic lookup
operations with high probability on Chord. The system described in the previous
section allows any node to obtain its DHT key and its region key, in a fully
distributed manner, just by applying a consistent hash function. Using an RPC
call in Chord, the node can obtain the region's master node, called
\emph{Cluster Node (CN)} which is responsible for clustering the nodes belonging
in the same sector or region with that of the node at hand. An additional RPC
call, registers it to its corresponding region and publishes its information,
through the special peer CN. The node can, additionaly, ask CN for other
nodes that have previously joined the region in order to add them into its
neighbour set for future routing table optimization. Even in the case when no
neighbour is detected in the current region, the search is expanded to adjasent
regions and towards an upper layer identifier space until one is found or the
first layer reached.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Quasi-Chord}
The approach that is proposed by Sun and Zhang in \cite{sun_quasi_2008}
confronts the topology mismatch problem, in the Chord DHT context which, in its
vanilla version, takes no consiteration for the underlying physical network
topology during the construction of the identifier cycle. To construct a
\emph{Quasi-Chord} network three steps are followed needed. First, each host
acquires its coordinates in the geometric space utilizing the \emph{global
network position (GNP)} protocol \cite{ng_gnp_2001}. Second, using the
\emph{Cantor space filling curve}, the $2$-dimensional space is converted to a
$1$-dimensional one, used in the last, third, step to build the Quasi-Chord
circle according to the host's Cantor value.

%In the following paragraphs, these steps are furtherly discussed.
%
%\paragraph{GNP coordinates}
%First of all the host must be positioned in the geometric space. The algoritm
%  models the P2P network with a well defined distance function in such a way,
% it can predict, with high accuracy, the distance between any two points in the
% space by just evaluating the output of the distance function on the
% coordinates of these points. This is accomplished with the \emph{global
% network position (GNP)} protocol which\begin{inparaenum}[\itshape i\upshape)]
%  \item creates a reference set of $N$ landmark nodes so as to minimize the
%  error of ICMP measured distances and coordinate computed ones between them,
% and then
%  \item each host is able to measure its round-trip times to the $N$ Landmarks
% in order to compute its own coordinates.
%\end{inparaenum}
%
%\paragraph{Cantor SPF}
%After the $2$-d coordinates are set, in the next stage of the algorithn, each
%  participating peer is assigned a Cantor value, according to the application
% of a \emph{space filling curve} on the coordinate space. (TODO: add figure).
% This results in the conversion of the $2$-dimensional space to a
% $1$-dimensional Cantor space that can more easily be more mapped to the Chord
% hierarchy.
%
%\paragraph{Quasi-Chord construction}
%As can intuitively be infered by observing the Cantor chart, close-by nodes in
%  the physical layer, are more likely to have similar Cantor values. This
% attribute is exploited in order to construct a topology-aware identifier space
% for the Chord DHT. The cycle is constructed by sorting nodes in ascending
% order. Each host maintains 2 finger tables, one for clockwise and one for
% counter-clockwise stepping. This helps with the connectivity of the network
% because its not allowed to connect the first node with the last one since this
% will incur heavy traffic to the later\footnote{After all their Cantor values
% denote that they are actually the furthest of each other.}.
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{IP-based Clustering (IPBC)}
Proximity neighbour selection algorithms use probing and other techniques to
detect proximity. However, such methods are either not precise enough, or
overload the network. \emph{IP-based clustering} \cite{karwaczynski_ipbc_2007}
is a proximity neighbour selection based algorithm in which the authors propose
to use the IP address prefixes (16 bit for IPv4) in order to detect proximity.
\cite{freedman_iploc_2005} states that $97\%$ of prefixes larger than $24$ bits
belong to a single geographical location. However, using less number of bits
creates less precise results and more number of bits increase the burden on the
network and reduce the possible number of neighbours. Therefore, a careful
selection is required in terms of performance/accuracy tradeoff. IP-based
Clustering generates a key and its prefix and stores the later in the DHT
itself, so that any newly joining nodes with the same IP prefix can query it and
identify all the neighbours with the same one relatively easy. Nodes
periodically update their entries in the DHT by removing those who leave, or
those who has been timed out with no further activity detected from the node.
